\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{url, hyperref, multicol, xcolor, enumerate}
\setlength{\parindent}{0cm}


\begin{document}
\begin{center} \Large \bf
  Review of Paradoxical Coastal Property Value Resilience Amid
2 Climate Risks by Jack Bienvenue
\end{center}


Great work Jack! This is clearly a well-written and well-thought-out paper with relevant analysis for the question at hand. You did a great job clearly explaining the steps you took during the analysis and the paper flows very nicely. The tables and figures also aid in understanding the material. Specifically the excerpts explaining the regional encoding data. I think this would be difficult to understand without seeing examples, Nice! This is a nice piece of scholarly work and is a great place to be for a first draft!\\

My major and minor concerns are listed below.\\

\noindent Major concerns:

N/A


\noindent Minor concerns:

\begin{itemize}

\item I thought the introduction was very well written and very clearly explained the question you're trying to answer. I know you mention McNamara's work, but maybe there could be a little more explanation as to how your work is different from or adds to existing work. Although this may not be necessary as it sounds good the way it is.

\item Line 53: 'This analysis will build a method for independently verifying or the assertion made in McNamara et al. (2024)', Something grammatical going on here.

\item Line 131: '...other subsampling methods have been proposed in the field os statistics for optimizing...', I think 'os', should be 'of'.

\item Line 166: 'This analysis finds that there is no statistical evidence suggesting that there is no discrepancy between the average monthly changes in coastal and non-coastal real estate valuations', I think it should be 'This analysis finds that there is no statistical evidence suggesting that there is a discrepancy...'. 

\item Line 185: '...intensified storms have experience transitory or long lasting home valuations effects...', 'experience' --$>$ 'experienced'

\item Line 186-187: '...peer counties which did not experience extreme damages from climatic trends.', 'did not experience' ---$>$ 'have not experienced'


\end{itemize}




%\bibliography{refs}
%\bibliographystyle{mcap} 

\end{document}